Drawing Math

### 2022-05-08 paper/Paper.tex
prog

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\seedAngle}[1]{{\theta_{#1}}^j}
\newcommand{\seedAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}

@@

Now that we have our machinery built up, lets define $Comb: \mathcal{S}^k \rightarrow \R^d$ such that
$$
  \Delta p_{i + 1} = Comb\left(s^1_{i + 1}, s^2_{i + 1}, ..., s^k_{i + 1}\right).
$$
In other words, $Comb$ takes in the state of each seed and
returns an update to the position of the turtle.

@@

\subsection{Some more restrictions on our problem}
We further restrict the problem by only considering the case where
$$
  Comb((., ., ., ., \theta^1), (., ., ., ., \theta^2), ..., (., ., ., ., \theta^k)) =
    \left(\prod_{i=1}^k \cos(\theta_j) ^ {\mathrm{incl}_1^j}, ..., \prod_{i=1}^k \cos(\theta_j) ^ {\mathrm{incl}_D^j}\right)
$$
where $\mathrm{incl}_d^j \in \set{0, 1}$ for $d \in [D]$ indicates whether to include a given
$x \in R$ determined by seed $j$ for position update in the $d$th dimension.

@@

@@

Moreover, define function $\mathrm{digSumPeriodic}: \N^4 \rightarrow \Z_b$
such that
% TODO: define T within the func from another func
\begin{equation}
  \mathrm{digSumPeriodic}(n, d, b) = \sum_{i = i_0}^{i_0 + T} \mathrm{digit}(n, d, b, i)
\end{equation}

@@

\subsubsection{Finding the period of $\seedAngleNotime$} % TODO: redifine things in terms of theta...
For $(n^j, b^j, d^j, \theta_i^j) = s_i^j$,
recall that $\seedAngle{i + 1} = \seedAngle{i} + \mathrm{digit}(n, b, d, i) \mod b$.
So, after period $\rationalPeriod$,
\begin{align*}
  \theta_{i + \rationalPeriod} &= \left(\theta_{i} + \sum_{\ell = i}^{\rationalPeriod + i} \mathrm{digit}(n, b, d, \ell)\right) \mod b\\
  &= \left(\theta_{i} + \mathrm{digSumPeriodic}(n, b, d)\right) \mod b\\
  &= \theta_{i} \mod b + \mathrm{digSumPeriodic}(n, b, d) \mod b.
\end{align*}
So, after $p$ periods of length $\rationalPeriod$ where $p \cdot \mathrm{digSumPeriodic}(n, b, d) \equiv 0 \mod b$,
$$
\theta_{i + p\rationalPeriod} = \theta_i.
$$
For simplicity, lets define
$$
  T^j = p\rationalPeriod
$$
where $T^j$ is the period of the state for seed $j$.
TODO: remove $i$ from the state and somehow have it be implicit....

\subsubsection{Finding the period of $\pmb{s}$}
We can first see that for $\stateNotime{j} \in \pmb{s}$, $\stateNotime{j}$
has period of $\statePeriod$. So, $\pmb{s}$ must have a period, $\totalPeriod$, of
$$
\lcm{j \in [k]}\; T^j.
$$
I.e.\ $\pmb{s}_i = \pmb{s}_{i + T}$ for all $i \in \N$.

@@

% \subsection{$\Delta P_{i, i + T} = 0$?}
% A bunch of sums and multiplies
% \cite{watrous2018theory}

@@

>>>>

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\rationalPeriodTotal}{{T}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\seedAngle}[1]{{\theta^j_{#1}}}
\newcommand{\seedAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}
\newcommand{\totalState}{\pmb{s}_i}
\newcommand{\totalStateNotime}{\pmb{s}}
\newcommand{\comb}{Comb}
\newcommand{\combWithState}[1]{Comb\left(s^1_{#1}, s^2_{#1}, ..., s^k_{#1}\right)}
\newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos(\theta_j) ^ {\inclIndic{#1}{j}}}
\newcommand{\digSumPeriodic}{\mathrm{digSumPeriodic}^j}

@@

Now that we have our machinery built up, lets define $Comb: \mathcal{S}^k \rightarrow \R^d$ such that
$$
  \Delta p_{i + 1} = \combWithState{i + 1}.
$$
In other words, $Comb$ takes in the state of each seed and
returns an update to the position of the turtle.

@@

\subsection{Some more restrictions on our problem}
We further restrict the problem by only considering the case where
$$
  Comb((., ., ., ., \theta^1), (., ., ., ., \theta^2), ..., (., ., ., ., \theta^k)) =
    \left(\combSingleTerm{1}, ..., \combSingleTerm{D}\right)
$$
where $\mathrm{incl}_d^j \in \set{0, 1}$ for $d \in [D]$ indicates whether to include a given
$x \in R$ determined by seed $j$ for position update in the $d$th dimension.

@@

Next, let $$
\rationalPeriodTotal = \lcm{j \in [k]}\; \rationalPeriod.
$$

@@

Moreover, define function $\mathrm{digSumPeriodic}: \N^4 \rightarrow \Z_b$
such that
% TODO: define T within the func from another func
% TODO: bettr defn
\begin{equation}
  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriod} \mathrm{digit}(n, d, b, i)
\end{equation}

@@

\subsubsection{Finding a period of $\seedAngleNotime$} % TODO: redifine things in terms of theta...
For $(n^j, b^j, d^j, \theta_i^j) = s_i^j$,
recall that $\seedAngle{i + 1} = \seedAngle{i} + \mathrm{digit}(n, b, d, i) \mod b$.
So, after period $\rationalPeriodTotal$,
\begin{align*}
  \theta_{i + \rationalPeriodTotal} &= \left(\theta_{i} + \sum_{\ell = i}^{\rationalPeriodTotal + i} \mathrm{digit}(n, b, d, \ell)\right) \mod b\\
  &= \left(\theta_{i} + \frac{\rationalPeriodTotal}{\rationalPeriod} \digSumPeriodic\right) \mod b\\
  &= \theta_{i} \mod b + \frac{\rationalPeriodTotal}{\rationalPeriod} \digSumPeriodic \mod b.
\end{align*}
So, after $p$ periods of length $\rationalPeriodTotal$ where $p \cdot \frac{\rationalPeriodTotal}{\rationalPeriod}  \cdot \digSumPeriodic \equiv 0 \mod b$,
$$
\theta_{i + p\rationalPeriodTotal} = \theta_i.
$$
For simplicity, lets define
$$
  T^j = p\rationalPeriodTotal
$$
where $T^j$ is a period of the state for seed $j$.
% TODO: remove $i$ from the state and somehow have it be implicit....

% Oh man... we are going to have to define an intermediate total period...
% One for all T'...
% and then have a sum for T
\subsubsection{Finding the period of $\pmb{s}$}
We can first see that for $\stateNotime{j} \in \pmb{s}$, $\stateNotime{j}$
has period of $\statePeriod$. So, $\pmb{s}$ must have a period, $\totalPeriod$, of
$$
\lcm{j \in [k]}\; T^j.
$$
I.e.\ $\pmb{s}_i = \pmb{s}_{i + T}$ for all $i \in \N$.

@@

\subsection{Does it close? $\Delta P_{i, i + T} = 0$?}
So now that we know the period of $\totalStateNotime$, we can ask if
$\Delta P_{i, i + T} = 0$. % TODO: reference

Note that 
$$
\Delta P_{i, i + T} = \Delta P_{q, q + T}
$$
for all $i, q \in \N$ by definition of periodicity.
So, we will drop the $i$ and replace it with a $0$.
Then,
\begin{align*}
  \Delta P_{0, T} &= \sum_{i = 1}^T \Delta p_i \\
  &= \sum_{i = 1}^T \combWithState{i} \\
  &= \sum_{i = 1}^T \left(\combSingleTerm{1}, ..., \combSingleTerm{D}\right) \\
  &= \left(\sum_{i = 1}^T \combSingleTerm{1}, ..., \sum_{i = 1}^T \combSingleTerm{D}\right).
\end{align*}
We can thus see that $\Delta P_{0, T} = \pmb{0} = (0, ..., 0)$ iff 
\begin{equation}
\label{eq:singleDelta0}
\sum_{i = 1}^T \combSingleTerm{d} = 0
\end{equation}
for all $d \in D$.

\subsubsection{Closing along a single dimension}
Finally, to see if a shape will close,
we just need to find if equation \eqref{eq:singleDelta0} holds true for all dimensions.
First, let $A_d = \set{j \mid j \in [k] \and \inclIndic{d}{j} = 1}$
We can then see that
\begin{align*}
&\sum_{i = 1}^T \combSingleTerm{d}\\
&=\sum_{i = 1}^T \prod_{j = 1}^k \left(\half \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\right)^\inclIndic{d}{j}\\
&=2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
\end{align*}

\newcommand{\periodFrac}{\frac{\totalPeriod}{\rationalPeriod}}
\newcommand{\periodFracRational}{\frac{\rationalPeriodTotal}{\rationalPeriod}}

We can then see that for $(n, b, d, \theta_i) \in \pmb{s}_i$
\begin{align*}
  \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \\
  &= \sum_{p = 0}^{x\periodFrac - 1} \sum_{q=0}^{\rationalPeriod - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + b)
    + \sum_{p = 0}  \\
    % ARGS::....
  &= x\cdot \periodFracRational \cdot \digSumPeriodic + .
\end{align*}

Then, 
\begin{align*}
 &2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
 =& 2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right)\\
\end{align*}

% A bunch of sums and multiplies
% \cite{watrous2018theory}

@@

% TODO: put b\theta / 2pi in State UPDATE
